Summer 2025 ToDo

### 2025-07-11 Relations/Paper/Summer_2025_TODO.tex
reflecting  the agda standard library rewriting section

>>>>

\section*{Agda standard library}
\\ Some of the work we have explored is formalized in the Agda standard library.  
% https://agda.github.io/agda-stdlib/v1.7.3/Relation.Binary.Rewriting.html#2096
\begin{todolist}
  \item Write about the standard library formalization in our paper and talk about how ours differs. 
  \item Create an equivalences file showing that our formalization agrees with the ASL (specifically definitions such as confluet, wcr, nf, leading up to showing our formalizations of Newman's lemma agree).
  \item Investigate contributing work to the ASL. This may mean refactoring the work already done to conform with the ASL. Specific contributions would likely be: Generalized NL. Theorem's 122 and 123. Alternative definitions of Wellfounded. 
\end{todolist}
